Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
checkpoint, todo cleanup

This telemetry design is admittedly coarse-grained.
For instance, it does not distinguish between edits that ignore a type
error from edits that remove one error while introducing another.
We acknowledge this and other threats in~\cref{s:threats}.\todo{Do we?
Double check.}
The main advantages of this telemetry are the small size of each record
and complete the lack of private information.
Furthermore, despite the limitations, this telemetry supports a variety of
interesting conclusions that we showcase in the next section.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
Each vertical bar counts the number of records generated per hour according to
a client-side timestamp.\todo{Not just per day?!?}
The bars are labeled with a California time zone.
Buckets\todo{What is a BUCKET as opposed to a BAR?}
contain a few dozen to over 3,000 records, typically about 1,000.
%% \FILL{} investigate one tower, what's happening?? all one session?
Telemetry ended in early April; the long tail is due to developers
updating Roblox Studio later.
% BEN: I see no basis for this; nor is this at all interesting.
% We do not know which timezone the records originated in, but since the counts
% tend to peak midday California time it seems that the majority
% of Roblox developers are following a Western Hemisphere schedule.
The regular pattern of the peaks suggests that many creators
follow a regular schedule; these may be
professional developers.
The tall weekend (shaded) regions could be because
Roblox has a significant school-aged creator community.

@@

Digging further into \FS{} errors, the median number of such errors by mode is
1 in \mnocheck{}, 3 in \mnonstrict{}, and 1 in \mstrict{}.
Records in \mnocheck{} mode evidently do not have significantly more \FS{}
errors.
Furthermore, type analysis does not seem to reduce \FS{}
errors.\todo{Isn't this a bit surprising?}

@@

% BEN: double-check, I think this says all you were trying to say.
% "typically" because we COULD have gotten lucky.
The counts are imprecise because of telemetry granularity.
If a creator removes one error but then
immediately introduces another on a different line, this typically manifests as
a \keepsym{} rather than one \addsym{} and one \dropsym{}.

@@

Fifth, type analysis reports several errors at once and we have no idea which
errors, if any, creators intended to fix with their edits.
Thus, fixes may be a side effect of other plans, as seen in prior work~\cite{mfk-sigcse-2011}.
% This is the [DIFF] code from Marceau SIGCSE 2011.

>>>>

This telemetry design is admittedly coarse-grained.
For instance, it does not distinguish between edits that ignore a type
error from edits that remove one error while introducing another.
We acknowledge this and other threats in~\cref{s:threats}.
The main advantages of this telemetry are the small size of each record
and complete the lack of private information.
Furthermore, despite the limitations, this telemetry supports a variety of
interesting conclusions that we showcase in the next section.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
The x-axis is labeled with a California time zone; the thin vertical lines
mark the start of a new day.
Each of the blue bars in the plot bar is a bucket that counts the number of
records generated per hour according to a client-side timestamp.
Buckets contain a few dozen to over 3,000 records, typically about 1,000.
%% \FILL{} investigate one tower, what's happening?? all one session?
Telemetry ended in early April; the long tail is due to developers
updating Roblox Studio later.
% BEN: I see no basis for this; nor is this at all interesting.
%% ben: basis = it's where the peaks are
% We do not know which timezone the records originated in, but since the counts
% tend to peak midday California time it seems that the majority
% of Roblox developers are following a Western Hemisphere schedule.
The regular pattern of the peaks suggests that many creators
follow a regular schedule; these may be
professional developers.
The tall weekend (shaded) regions could be because
Roblox has a significant school-aged creator community.

@@

Digging further into \FS{} errors, the median number of such errors by mode is
1 in \mnocheck{}, 3 in \mnonstrict{}, and 1 in \mstrict{}.
Records in \mnocheck{} mode evidently do not have significantly more \FS{}
errors.
Furthermore, type analysis does not seem to reduce \FS{}
errors; this is surprising and~\cref{s:tefs-compass} has more to say about it.

@@

% BEN: double-check, I think this says all you were trying to say.
% "typically" because we COULD have gotten lucky.
% ben: I'd written "immediatly introduces" to rule out getting lucky. Deleted "immediately" and went with your version.
The counts are imprecise because of telemetry granularity.
If a creator removes one error but then
introduces another on a different line, this typically manifests as
a \keepsym{} rather than one \addsym{} and one \dropsym{}.

@@

Fifth, type analysis reports several errors at once and we have no idea which
errors, if any, creators intended to fix with their edits.
Thus, fixes may be a side effect of other plans, as seen in prior work~\cite{mfk-sigcse-2011}.
% This is the [DIFF] code from Marceau SIGCSE 2011.
Edits that fix one error but introduce another are also indistinguishable
from edits that maintain the number of errors.
